A Multi-Modal Model of Object Deformation under Robotic Pushing

### 2017-01-25 AnswersToComments-finalreview.tex

\address{Universidad Nacional Autónoma de México\\ Facultad de Ciencias,\\ Departamento de Matemáticas,\\ México, D.F.}
\telephone{5622 5426}

\opening{Dear Editors,}{\today}
\vspace{1cm}

Please find attached the pdf of our revised submission to the special issue on “Sensorimotor Contingencies for Cognitive Robotics”.

We would like to thank you and all reviewers for timely and informative reviews, and for the comments, which have helped us to substantially improve our paper. In this final revised version we address the comments from the two reviewers who still made observations. We detail below how we have addressed each reviewer point one by one.

We look forward to hearing from you.

@@

%%enclosure listing
%%\encl{}

\end{letter}

\textbf{Response to reviewers’ comments}

We would like to thank all the reviewers most sincerely for their effort in reading and commenting on our paper.  We address now their final remarks.

\textbf{Reviewer: 1}

{\calligra\large The authors have successfully modified the work according to the reviewers comments. In my opinion the work is ready to be published under one condition: equation 11 should be replaced with equation 23 from the appendix.}

Thanks to this observation we noticed an inconsistency between the text and the equations, which suggested we should include equation 23 were we had 11.  However, since all lengthy equations were moved to the appendix, instead of bringing equation 23 back, we arranged the text in section VI.A. so that only equations for the constraints would be shown here, and all derived forces could be found in the appendix.  We hope this will make the presentation clearer.

\textbf{Reviewer: 2}

{\calligra\large In this revision, the authors solved the major problems in previous manuscript, but there are several small problems:}

{\calligra\large 1, Equation (5) shows $F=m\frac{\partial p}{\partial t}$, but it seems that $F=m\frac{\partial^2 p}{\partial t^2}$ is more reasonable, since force equals mass multiplying acceleration. This problem remains in Equation (6) and the paragraph between Equation (5) and Equation (6).}

Sorry you are right, we mixed notation which was not used in the article where the momentum of the particle is defined as $p=mv$.  All the affected equations were modified to avoid this and keep $p$ as the position of the particle.

{\calligra\large 2, Equation (13) and Equation (14) are confusing. Is it a symbol conflict? Why does the derivative of $\vec{p}$ equal $\vec{p}$?}

It is a mathematical trick to force over damped systems of springs, which do not oscillate.  The text in this paragraph was modified to make this more explicit.  Also, we added a quick explanation about the differential equation of the form $f(x) = f'(x)$.

\end{document}

### 2017-01-25 twostagedo-rev-final.tex
Added cover letter for final review.

\begin{figure}[!t]
\centering
%\setlength\fboxsep{0.5pt}    % padding
%\setlength\fboxrule{0.5pt} % line width
%\fbox{
\includegraphics[width=3.5in]{figures/learning.png}%}
\caption{The visual tracking and force measurement system subserves the offline learning system. The offline learning (or calibration) method comprises two learned models of sensorimotor contingencies. Both are learned from the same data. The first (FP) learns to predict the force experienced for some motion and material. The second (SP) predicts the deformation of the object given the applied force. The strain $st$ is calculated directly from the interpenetration of the finger into the object. This can be calculated by vision (V) or from the planned motion of the finger.}
\label{fig:learning}
\end{figure}

@@

\begin{figure}[!t]
\centering
\includegraphics[width=3.5in]{sponge__result.jpg}
\caption{Neural network approach fits quite well the training data set, but can not generalise to new pushing actions.  The red line shows the border used as ground truth in the training set, while yellow lines show prediction from the FFNN.}\label{fig:cretu_prediction_sponge}
\end{figure}
\begin{figure}[!t]
\centering
\includegraphics[width=3.5in]{plasticine__result.jpg}
\caption{GNG segmentation didn't work with a shadowed material (video of plasticine). This image shows the segmentation results previous to the application the median filter, which was applied to perform tracking.  Results also do not generalise to unseen pushing actions.  The red line shows the border used as ground truth in the training set, while yellow lines show prediction from the FFNN.}\label{fig:cretu_prediction_plasticine}
\end{figure}

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.2in,clip,keepaspectratio]{arrio}}]{Veronica E. Arriola-Rios}
  has recently obtained her PhD in Computer Science from the University of Birmingham.
  She works as full time lecturer at the National Autonomous University of Mexico (UNAM).
  Veronica holds undergraduate degrees in Physics and Computer Science, and a masters degree in Computer Sciences, in the area of Computer Graphics and Virtual Environments.
  Her research interests include artificial inteligence, cognitive robotics and natural cognition.
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.2in,clip,keepaspectratio]{wyatt}}]{Jeremy L. Wyatt} is Professor of Robotics
  and Artificial Intelligence at the University of Birmingham. He
  obtained a BA in Theology from the University of Bristol, an MSc in
  Knowledge Based Systems from the University of Sussex, and his
  Ph.D. in Artificial Intelligence from the University of Edinburgh in
  1997. He was a Leverhulme Fellow from 2006-8. He has won two best paper prizes, published more than 100 refereed articles, led two international research projects on robot planning and learning (CogX) and robot manipulation (PaCMan), and edited three books. His interests
  include machine learning, planning, architectures, vision, mobile robotics and robot manipulation.
\end{IEEEbiography}

>>>>

\begin{figure}[!t]
\centering
%\setlength\fboxsep{0.5pt}    % padding
%\setlength\fboxrule{0.5pt} % line width
%\fbox{
\includegraphics[width=3.5in]{figures/learning}%}
\caption{The visual tracking and force measurement system subserves the offline learning system. The offline learning (or calibration) method comprises two learned models of sensorimotor contingencies. Both are learned from the same data. The first (FP) learns to predict the force experienced for some motion and material. The second (SP) predicts the deformation of the object given the applied force. The strain $st$ is calculated directly from the interpenetration of the finger into the object. This can be calculated by vision (V) or from the planned motion of the finger.}
\label{fig:learning}
\end{figure}

@@

\begin{figure}[!t]
\centering
\includegraphics[width=3.5in]{sponge__result}
\caption{Neural network approach fits quite well the training data set, but can not generalise to new pushing actions.  The red line shows the border used as ground truth in the training set, while yellow lines show prediction from the FFNN.}\label{fig:cretu_prediction_sponge}
\end{figure}
\begin{figure}[!t]
\centering
\includegraphics[width=3.5in]{plasticine__result}
\caption{GNG segmentation didn't work with a shadowed material (video of plasticine). This image shows the segmentation results previous to the application the median filter, which was applied to perform tracking.  Results also do not generalise to unseen pushing actions.  The red line shows the border used as ground truth in the training set, while yellow lines show prediction from the FFNN.}\label{fig:cretu_prediction_plasticine}
\end{figure}

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.2in,clip,keepaspectratio]{arrio.jpeg}}]{Veronica E. Arriola-Rios}
  has recently obtained her PhD in Computer Science from the University of Birmingham.
  She works as full time lecturer at the National Autonomous University of Mexico (UNAM).
  Veronica holds undergraduate degrees in Physics and Computer Science, and a masters degree in Computer Sciences, in the area of Computer Graphics and Virtual Environments.
  Her research interests include artificial inteligence, cognitive robotics and natural cognition.
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.2in,clip,keepaspectratio]{wyatt.jpeg}}]{Jeremy L. Wyatt} is Professor of Robotics
  and Artificial Intelligence at the University of Birmingham. He
  obtained a BA in Theology from the University of Bristol, an MSc in
  Knowledge Based Systems from the University of Sussex, and his
  Ph.D. in Artificial Intelligence from the University of Edinburgh in
  1997. He was a Leverhulme Fellow from 2006-8. He has won two best paper prizes, published more than 100 refereed articles, led two international research projects on robot planning and learning (CogX) and robot manipulation (PaCMan), and edited three books. His interests
  include machine learning, planning, architectures, vision, mobile robotics and robot manipulation.
\end{IEEEbiography}
